---
title: "Syracuse Poverty"
author: "Sam Edelstein"
date: "9/16/2018"
output: html_document
---

#Poverty in Syracuse

The City of Syracuse was recently cited as one of the top 10 poorest cities in the country by the US Census Bureau. The Census Bureau puts out a yearly survey of a sample of the population called the American Community Survey. They also put out a compiled American Community Survey that combines ACS data from the previous 5 years. The 1 year survey has information from fewer people so it doesn't get as granular as the 5 year survey, which often allows an analysis down to a census tract or census block group levels rather than only at a city-wide level.
```{r setup, include=FALSE}
library(censusapi)
library(ggplot2)
library(dplyr)
library(maptools)
library("gpclib")
library('rgdal')
library(scales)
require(sf)
library(tidyverse)
library(rvest)
Sys.setenv(CENSUS_KEY="6e16b11542b37f683e1a381a58b1a8172792c11b")
apis <- listCensusApis()

theme_map <- function(...) {
  theme_minimal() +
    theme(
      text = element_text(family = "Arial", color = "#22211d"),
      axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      # panel.grid.minor = element_line(color = "#ebebe5", size = 0.2),
      panel.grid.major = element_line(color = "#ebebe5", size = 0.2),
      panel.grid.minor = element_blank(),
      plot.background = element_rect(fill = "#f5f5f2", color = NA), 
      panel.background = element_rect(fill = "#f5f5f2", color = NA), 
      legend.background = element_rect(fill = "#f5f5f2", color = NA),
      panel.border = element_blank(),
      ...
    )
}
```

## Percent of people in poverty in Syracuse since 2011 (ACS 1-yr)
We can look at a history of poverty since the Census makes all of this data public. Here we can see that the City of Syracuse's poverty rate has fluctuated and has generally dropped, but remains in the mid-30s.

```{r poverty history, echo=FALSE}
p2017 <- getCensus(name="acs/acs1", vintage=2017,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                     vars=c("NAME", "B01001_001E","B17001_001E", 'B17001_002E'), 
                     region="place:*", regionin="state:36") %>%
  mutate(year = "2017")
p2016 <- getCensus(name="acs/acs1", vintage=2016,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B17001_001E", 'B17001_002E'), 
                   region="place:*", regionin="state:36") %>%
  mutate(year = "2016")
p2015 <- getCensus(name="acs/acs1", vintage=2015,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B17001_001E", 'B17001_002E'), 
                   region="place:*", regionin="state:36") %>%
  mutate(year = "2015")
p2014 <- getCensus(name="acs/acs1", vintage=2014,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B17001_001E", 'B17001_002E'), 
                   region="place:*", regionin="state:36") %>%
  mutate(year = "2014")
p2013 <- getCensus(name="acs/acs1", vintage=2013,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B17001_001E", 'B17001_002E'), 
                   region="place:*", regionin="state:36") %>%
  mutate(year = "2013")
p2012 <- getCensus(name="acs/acs1", vintage=2012,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B17001_001E", 'B17001_002E'), 
                   region="place:*", regionin="state:36") %>%
  mutate(year = "2012")
p2011 <- getCensus(name="acs/acs1", vintage=2011,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B17001_001E", 'B17001_002E'), 
                   region="place:*", regionin="state:36") %>%
  mutate(year = "2011")

poverty_rate_chart <- rbind(p2011, p2012, p2013, p2014, p2015, p2016, p2017) %>%
  filter(NAME == "Syracuse city, New York") %>%
  mutate(poverty_rate = round((B17001_002E/B17001_001E)*100)) %>%
  ggplot(aes(year, poverty_rate, group = NAME, color = NAME)) +
  geom_point() + 
  geom_line() +
  ylim(c(0,100)) +
  labs(title = "Percent of poverty in Syracuse since 2011",
       x = "Year",
       y = "Poverty rate (%)") +
  theme_minimal()
poverty_rate_chart
```

## Poverty by city in 2017
We can also compare against other cities to benchmark. Here we can see that Syracuse has one of the highest poverty rates in the state.
```{r poverty compared, echo=FALSE}
poverty_city_chart <- rbind(p2011, p2012, p2013, p2014, p2015, p2016, p2017) %>%
  filter(year == 2017) %>%
  mutate(poverty_rate = round((B17001_002E/B17001_001E)*100),
         ToHighlight = ifelse( NAME == "Syracuse city, New York", "yes", "no" ) ) %>%
  ggplot(aes(reorder(NAME, poverty_rate), poverty_rate, fill = ToHighlight)) +
  geom_col() +
  coord_flip() + 
  ylim(c(0,100)) +
  scale_fill_manual( values = c( "yes"="tomato", "no"="gray" ), guide = FALSE ) +
  geom_text(aes(label=paste(poverty_rate, "%", sep = ""), hjust=1.25))+
  labs(title = "Poverty rates by city across New York State",
       x = "",
       y = "") +
  theme_bw() +
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "grey"), axis.text.x=element_blank(),axis.ticks.x=element_blank(),
          axis.title.x=element_blank())
poverty_city_chart
```



## Public Transportation History
We can also look at specific measures, like how many people take public transportation - or even more detailed - how many people in poverty take public transportation.

```{r public transportation poverty history, echo = FALSE}
t2017 <- getCensus(name="acs/acs1", vintage=2017,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B08119_028E", "B08119_029E", "B08119_030E", "B08119_031E", "B08101_001E", 'B08101_025E'), 
                   region="place:*", regionin="state:36") %>%
  rename("total_pop" = B01001_001E, "total_pub_trans" = B08119_028E, "total_pub_trans_1_9999" = B08119_029E, "total_pub_trans_10k_14999" = B08119_030E, "total_pub_trans_15k_24999" = B08119_031E, "total_trans" = B08101_001E, "total_pub" = B08101_025E) %>%
  mutate(year = "2017",
         poverty_pub_transp = rowSums(select(., total_pub_trans_1_9999,total_pub_trans_10k_14999, total_pub_trans_15k_24999)),
         percent_poverty_pub_transp = round((poverty_pub_transp/total_pub)*100),
         percent_pub_transport = round((total_pub/total_trans)*100))

t2016 <- getCensus(name="acs/acs1", vintage=2016,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B08119_028E", "B08119_029E", "B08119_030E", "B08119_031E", "B08101_001E", 'B08101_025E'), 
                   region="place:*", regionin="state:36") %>%
  rename("total_pop" = B01001_001E, "total_pub_trans" = B08119_028E, "total_pub_trans_1_9999" = B08119_029E, "total_pub_trans_10k_14999" = B08119_030E, "total_pub_trans_15k_24999" = B08119_031E, "total_trans" = B08101_001E, "total_pub" = B08101_025E) %>%
  mutate(year = "2016",
         poverty_pub_transp = rowSums(select(., total_pub_trans_1_9999,total_pub_trans_10k_14999, total_pub_trans_15k_24999)),
         percent_poverty_pub_transp = round((poverty_pub_transp/total_pub)*100),
         percent_pub_transport = round((total_pub/total_trans)*100))

t2015 <- getCensus(name="acs/acs1", vintage=2015,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B08119_028E", "B08119_029E", "B08119_030E", "B08119_031E", "B08101_001E", 'B08101_025E'), 
                   region="place:*", regionin="state:36") %>%
  rename("total_pop" = B01001_001E, "total_pub_trans" = B08119_028E, "total_pub_trans_1_9999" = B08119_029E, "total_pub_trans_10k_14999" = B08119_030E, "total_pub_trans_15k_24999" = B08119_031E, "total_trans" = B08101_001E, "total_pub" = B08101_025E) %>%
  mutate(year = "2015",
         poverty_pub_transp = rowSums(select(., total_pub_trans_1_9999,total_pub_trans_10k_14999, total_pub_trans_15k_24999)),
         percent_poverty_pub_transp = round((poverty_pub_transp/total_pub)*100),
         percent_pub_transport = round((total_pub/total_trans)*100))

t2014 <- getCensus(name="acs/acs1", vintage=2014,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B08119_028E", "B08119_029E", "B08119_030E", "B08119_031E", "B08101_001E", 'B08101_025E'), 
                   region="place:*", regionin="state:36") %>%
  rename("total_pop" = B01001_001E, "total_pub_trans" = B08119_028E, "total_pub_trans_1_9999" = B08119_029E, "total_pub_trans_10k_14999" = B08119_030E, "total_pub_trans_15k_24999" = B08119_031E, "total_trans" = B08101_001E, "total_pub" = B08101_025E) %>%
  mutate(year = "2014",
         poverty_pub_transp = rowSums(select(., total_pub_trans_1_9999,total_pub_trans_10k_14999, total_pub_trans_15k_24999)),
         percent_poverty_pub_transp = round((poverty_pub_transp/total_pub)*100),
         percent_pub_transport = round((total_pub/total_trans)*100))

t2013 <- getCensus(name="acs/acs1", vintage=2013,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B08119_028E", "B08119_029E", "B08119_030E", "B08119_031E", "B08101_001E", 'B08101_025E'), 
                   region="place:*", regionin="state:36") %>%
  rename("total_pop" = B01001_001E, "total_pub_trans" = B08119_028E, "total_pub_trans_1_9999" = B08119_029E, "total_pub_trans_10k_14999" = B08119_030E, "total_pub_trans_15k_24999" = B08119_031E, "total_trans" = B08101_001E, "total_pub" = B08101_025E) %>%
  mutate(year = "2013",
         poverty_pub_transp = rowSums(select(., total_pub_trans_1_9999,total_pub_trans_10k_14999, total_pub_trans_15k_24999)),
         percent_poverty_pub_transp = round((poverty_pub_transp/total_pub)*100),
         percent_pub_transport = round((total_pub/total_trans)*100))

t2012 <- getCensus(name="acs/acs1", vintage=2012,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B08119_028E", "B08119_029E", "B08119_030E", "B08119_031E", "B08101_001E", 'B08101_025E'), 
                   region="place:*", regionin="state:36") %>%
  rename("total_pop" = B01001_001E, "total_pub_trans" = B08119_028E, "total_pub_trans_1_9999" = B08119_029E, "total_pub_trans_10k_14999" = B08119_030E, "total_pub_trans_15k_24999" = B08119_031E, "total_trans" = B08101_001E, "total_pub" = B08101_025E) %>%
  mutate(year = "2012",
         poverty_pub_transp = rowSums(select(., total_pub_trans_1_9999,total_pub_trans_10k_14999, total_pub_trans_15k_24999)),
         percent_poverty_pub_transp = round((poverty_pub_transp/total_pub)*100),
         percent_pub_transport = round((total_pub/total_trans)*100))

t2011 <- getCensus(name="acs/acs1", vintage=2011,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B08119_028E", "B08119_029E", "B08119_030E", "B08119_031E", "B08101_001E", 'B08101_025E'), 
                   region="place:*", regionin="state:36") %>%
  rename("total_pop" = B01001_001E, "total_pub_trans" = B08119_028E, "total_pub_trans_1_9999" = B08119_029E, "total_pub_trans_10k_14999" = B08119_030E, "total_pub_trans_15k_24999" = B08119_031E, "total_trans" = B08101_001E, "total_pub" = B08101_025E) %>%
  mutate(year = "2011",
         poverty_pub_transp = rowSums(select(., total_pub_trans_1_9999,total_pub_trans_10k_14999, total_pub_trans_15k_24999)),
         percent_poverty_pub_transp = round((poverty_pub_transp/total_pub)*100),
         percent_pub_transport = round((total_pub/total_trans)*100))

poverty_pub_trans_chart <- rbind(t2017,t2016,t2015,t2014,t2013,t2012,t2011) %>%
    filter(NAME == 'Syracuse city, New York') %>%
  select(year, percent_poverty_pub_transp, percent_pub_transport) %>%
  gather(key = percent_pub_transport, value = "number", -year) %>%
  ggplot(aes(year, number, color = percent_pub_transport, group = percent_pub_transport)) +
  geom_line() +
  ylim(c(0,100)) +
  scale_color_manual(labels = c("Percentage of people in \npoverty who take \npublic transportation", "Percent of population \nwho takes \npublic transportation"), values = c("tomato", "blue")) +
  labs(title = "Percent of people riding public transportation",
       color = "Legend",
       x = "Year",
       y = "Percentage") +
  theme_minimal()

  
poverty_pub_trans_chart
```

## Public transportation by city
And again we can compare by city

```{r public transport city, echo = FALSE}
city_transport <- t2017 %>%
  select(NAME, percent_poverty_pub_transp, percent_pub_transport) %>%
  gather(key = percent_pub_transport, value = "number", -NAME) %>%
  filter(!is.na(number)) %>%
  mutate( ToHighlight = ifelse( NAME == "Syracuse city, New York", "yes", "no" ) ) %>%
  ggplot(aes(NAME, number, fill = ToHighlight)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=paste(number, "%", sep = ""), hjust=-.25))+
  coord_flip() +
  scale_fill_manual( values = c( "yes"="tomato", "no"="gray" ), guide = FALSE ) +
  labs(title = "Percent of people riding public transportation",
       color = "Legend",
       x = "City",
       y = "Percentage") +
  facet_wrap(~percent_pub_transport) +
  ylim(c(0,100))  +
  theme_bw() +
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "grey"), axis.text.x=element_blank(),axis.ticks.x=element_blank(),
          axis.title.x=element_blank())
city_transport
```

## Map of public transportation ridership

```{r public transportation map, echo = FALSE}
list.files('/Users/samedelstein/city_of_syracuse_poverty', pattern='\\.shp$')
census_tracts <- readOGR(dsn=path.expand("/Users/samedelstein/city_of_syracuse_poverty"), "Census_Tracts_in_Syracuse_NY_2010")
census_tracts@data$id <- row.names(census_tracts@data)
map_data_fortified <- fortify(census_tracts) 
fortified_join <- merge(map_data_fortified, census_tracts@data, by="id")

streets <- readOGR(dsn=path.expand("/Users/samedelstein/city_of_syracuse_poverty"), "City_Streets_2011")
streets@data$id <- row.names(streets@data)
streets_data_fortified <- fortify(streets) 
streets_fortified_join <- merge(streets_data_fortified, streets@data, by="id")

pub_trans_tract <- getCensus(name="acs/acs5", vintage=2016,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B08119_028E", "B08119_029E", "B08119_030E", "B08119_031E", "B08101_001E", 'B08101_025E'), 
                   region="tract:*", regionin="state:36+county:067") %>%
  rename("total_pop" = B01001_001E, "total_pub_trans" = B08119_028E, "total_pub_trans_1_9999" = B08119_029E, "total_pub_trans_10k_14999" = B08119_030E, "total_pub_trans_15k_24999" = B08119_031E, "total_trans" = B08101_001E, "total_pub" = B08101_025E) %>%
  mutate(year = "2017",
         poverty_pub_transp = rowSums(select(., total_pub_trans_1_9999,total_pub_trans_10k_14999, total_pub_trans_15k_24999)),
         percent_poverty_pub_transp = round((poverty_pub_transp/total_pub)*100),
         percent_pub_transport = round((total_pub/total_trans)*100),
         tractid = paste(state, county, tract, sep = ""))


censusmerge <- merge(fortified_join, pub_trans_tract, by.x = "GEOID10", by.y = "tractid")
censusmerge <- censusmerge[order(censusmerge$order),]

poverty_pub_transport_map <- ggplot() +
  geom_polygon(data = censusmerge, aes(x = long, y = lat, group = group, fill = percent_poverty_pub_transp), 
               color =NA, size = 0.25) +
      geom_path(data = streets_data_fortified, aes(x = long, y = lat, group = group), alpha = .25, color = "black") + 

  coord_fixed(1.3) +
  scale_fill_continuous(low = "grey", high = "tomato") +
  theme_map() 
poverty_pub_transport_map

```

## Percent public transportation overall

```{r, echo=FALSE}
pub_transport_map<- ggplot() +
  geom_polygon(data = censusmerge, aes(x = long, y = lat, group = group, fill = percent_pub_transport), 
               color = NA, size = 0.25) +
    geom_path(data = streets_data_fortified, aes(x = long, y = lat, group = group), alpha = .25, color = "black") + 

  coord_fixed(1.3) +
  scale_fill_continuous(low = "grey", high = "tomato") +
  theme_map() 
pub_transport_map
```



## Percent of people with computer science or math degrees

```{r compsci, echo = FALSE}
comp_sci <- getCensus(name="acs/acs5", vintage=2016,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B15012_001E", "B15012_002E"), 
                   region="tract:*", regionin="state:36+county:067") %>%
  mutate(percent_comp_math = round((B15012_002E/B15012_001E)*100),
         tractid = paste(state, county, tract, sep = ""))


censusmerge_compsci <- merge(fortified_join, comp_sci, by.x = "GEOID10", by.y = "tractid")
censusmerge_compsci <- censusmerge_compsci[order(censusmerge_compsci$order),]

ggplot() +
  geom_polygon(data = censusmerge_compsci, aes(x = long, y = lat, group = group, fill = percent_comp_math), 
               color = NA, size = 0.25) +
    geom_path(data = streets_data_fortified, aes(x = long, y = lat, group = group), alpha = .25, color = "grey") + 

  coord_fixed(1.3) +
  scale_fill_continuous(low = "grey", high = "tomato") +
  theme_map() 

```


## No schooling by census tract

```{r schooling, echo = FALSE}
schooling <- getCensus(name="acs/acs5", vintage=2016,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME", "B01001_001E","B15003_001E", "B15003_002E", "B15003_003E", "B15003_004E", "B15003_005E",
                          "B15003_006E","B15003_007E", "B15003_008E", "B15003_009E", "B15003_010E", "B15003_011E",
                          "B15003_012E","B15003_013E", "B15003_014E", "B15003_015E", "B15003_016E", "B15003_017E",
                          "B15003_018E","B15003_019E", "B15003_020E", "B15003_021E", "B15003_022E", "B15003_023E",
                          "B15003_024E","B15003_025E"),
                   region="tract:*", regionin="state:36+county:067") %>%
  mutate(tractid = paste(state, county, tract, sep = ""),
         percent_no_school= round((B15003_002E/B15003_001E)*100),
         sum_less_then_hs = rowSums(select(., B15003_002E,B15003_003E, B15003_004E, B15003_005E, B15003_006E,
                                           B15003_007E, B15003_008E, B15003_009E, B15003_010E, B15003_011E, B15003_012E)),
         percent_less_hs = round((sum_less_then_hs/B15003_001E)*100),
         sum_hs_no_degree = rowSums(select(., B15003_002E,B15003_003E, B15003_004E, B15003_005E, B15003_006E,
                                           B15003_007E, B15003_008E, B15003_009E, B15003_010E, B15003_011E, B15003_012E, B15003_013E,B15003_014E,B15003_015E,B15003_016E)),
         percent_no_hs_degree = round((sum_hs_no_degree/B15003_001E)*100))

censusmerge_schooling <- merge(fortified_join, schooling, by.x = "GEOID10", by.y = "tractid")
censusmerge_schooling <- censusmerge_schooling[order(censusmerge_schooling$order),]

no_schooling_chart <- ggplot() +
  geom_polygon(data = censusmerge_schooling, aes(x = long, y = lat, group = group, fill = percent_no_school), 
               color = NA, size = 0.25) +
    geom_path(data = streets_data_fortified, aes(x = long, y = lat, group = group), alpha = .25, color = "grey") + 

  coord_fixed(1.3) +
  scale_fill_continuous(low = "grey", high = "tomato") +
  theme_map() +
  labs(title = "No schooling")
no_schooling_chart



```

## Less than high school education

```{r, echo = FALSE}
less_than_hs_chart <- ggplot() +
  geom_polygon(data = censusmerge_schooling, aes(x = long, y = lat, group = group, fill = percent_less_hs), 
               color = "grey", size = 0.25) +
    geom_path(data = streets_data_fortified, aes(x = long, y = lat, group = group), alpha = .25, color = "grey") + 
  coord_fixed(1.3) +
  scale_fill_continuous(low = "grey", high = "tomato") +
  theme_map()  +
  labs(title = "No HS")
less_than_hs_chart
```

## No hs degree map

```{r, echo = FALSE}
no_hs_degree_chart <- ggplot() +
  geom_polygon(data = censusmerge_schooling, aes(x = long, y = lat, group = group, fill = percent_no_hs_degree), 
               color = NA, size = 0.25) +
    geom_path(data = streets_data_fortified, aes(x = long, y = lat, group = group), alpha = .25, color = "grey") + 
  coord_fixed(1.3) +
  scale_fill_continuous(low = "grey", high = "tomato") +
  theme_map() +
  labs(title = "No HS Degree")
no_hs_degree_chart
```

## Percentage of people with computers and internet connectivity

```{r connectivity, echo = FALSE}
getCensus(name="acs/acs1/profile", vintage=2017,  key = "6e16b11542b37f683e1a381a58b1a8172792c11b",
                   vars=c("NAME",'DP02_0150E',"DP02_0151E", "DP02_0152E"), 
                   region="place:*", regionin="state:36") %>%
  mutate(percent_computer = round((DP02_0151E/DP02_0150E)*100),
         percent_internet = round((DP02_0152E/DP02_0150E)*100)) %>%
  select(NAME, percent_computer, percent_internet) %>%
  gather(key = variable, value = "percent", -NAME) %>%
  mutate(ToHighlight = ifelse( NAME == "Syracuse city, New York", "yes", "no" ) ) %>%
  ggplot(aes(NAME, percent, fill = ToHighlight)) +
  geom_col(position = "dodge") +
  geom_text(aes(label=paste(percent, "%", sep = ""), hjust=1.25)) +
  scale_fill_manual( values = c( "yes"="tomato", "no"="gray" ), guide = FALSE ) +
  coord_flip() +
  ylim(c(0,100)) +
  facet_wrap(~variable)  +
  theme_bw() +
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "grey"), axis.text.x=element_blank(),axis.ticks.x=element_blank(),
          axis.title.x=element_blank())

```

## Lived in the same house 1 year ago

```{r same house , echo=FALSE}
probs <- c(0, 0.25, 0.5, 0.75, 1)
same_house <- getCensus(name="acs/acs5", vintage=2016, key = "6e16b11542b37f683e1a381a58b1a8172792c11b", 
                         vars=c("NAME", "B07001_017E", 'B07001_018E','B07001_019E','B07001_001E', 'B07001_002E','B07001_003E'), 
                         region="tract:*", regionin="state:36+county:067") %>%
  mutate(tot_moved_below_18 = rowSums(select(., B07001_018E,B07001_019E)),
         tot_below_18 = rowSums(select(., B07001_002E,B07001_003E)))  %>%
  mutate(percentage = round((tot_moved_below_18/tot_below_18)*100),
         tractid = paste(state, county, tract, sep = ""))
quantiles <- quantile(same_house$percentage, prob=probs, na.rm = TRUE)
same_house$quant <- factor(findInterval(same_house$percentage,quantiles))

censusmerge_same_house <- merge(fortified_join, same_house, by.x = "GEOID10", by.y = "tractid")
censusmerge_same_house <- censusmerge_same_house[order(censusmerge_same_house$order),]

same_house_map <- ggplot() +
  geom_polygon(data = censusmerge_same_house, aes(x = long, y = lat, group = group, fill = quant), 
               color = NA, size = 0.25) +
  geom_path(data = streets_data_fortified, aes(x = long, y = lat, group = group), alpha = .25, color = "darkgrey") + 
  coord_fixed(1.3) +
  theme_map() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Same house")
same_house_map

```


